SSwAB-IT Phase 1 Analysis

### 2024-04-15 Jordana Hoppe/SSwAB-IT/phase_1_analysis.qmd
updates for Jordana

```{r setup}
#| include: false
library(redcapAPI)
library(tidyverse)
library(gt)
library(gtsummary)
library(caret)
library(vcd)
library(eulerr)
```

@@

For these agreement analyses, we reported accuracy metrics that include all samples. Accuracy is the proportion of samples where the two tests agreed (positive/positive and negative/negative). Cohen's kappa accounts for agreement between the two tests by chance, and is interpreted analagously to correlation where -1 indicates perfect disagreement and 1 indicates perfect agreement. Cohen's kapps of NaN or NA indicates a lack of variability between the two tests.

>>>>

```{r setup}
#| include: false
library(redcapAPI)
library(tidyverse)
library(gt)
library(gtsummary)
library(caret)
library(twoxtwo)
library(vcd)
library(eulerr)
```

@@

For these agreement analyses, we reported accuracy metrics that include all samples. Accuracy is the proportion of samples where the two tests agreed (positive/positive and negative/negative). Cohen's kappa accounts for agreement between the two tests by chance, and is interpreted analogously to correlation where -1 indicates perfect disagreement and 1 indicates perfect agreement. A Cohen's kappa of NaN or NA indicates a lack of variability between the two tests.
